### 2022-05-08 methods.tex
General fleshing out, refinement and fixes.

In this chapter we discuss our solution to the problem of predicting solar power production. We cover the data we had access to and ultimately selected to train the neural network with and how we processed and structured the data. We explain the Temporal Fusion Transformer architecture and how we set it up and use it to achieve our goals.

@@

\subsection{Irradiance measurements}
The irradiance was measured with seven Kipp \& Zonen CM21 pyranometers placed around the power station. The pyranometers have a reported maximum measurement error of 3\%. For input into the network, the highest and lowest measured values are dropped and the average value of the other five measurements is used. This data is provided with five-minute intervals, but the neural network operates hourly. To downsample the measurement data to an hourly format, we averaged the values for the twenty minutes before and after the top of each hour. Finally, the irradiance values were normalized linearly to the range $0.0-1.0$ before input into the neural network.

\subsection{Forecast Data\label{cha:forecast_data}}
The weather forecast data is provided by Belgingur ehf., Reykjavik, Iceland. We use irradiance values from historical 24-hour weather forecasts generated by their WRF model, discussed in Section~\ref{cha:WRF}. The forecasts have a temporal resolution of one hour and a spatial resolution of 2.5km. One of our models uses forecast data from a 3x3 grid centred on the solar power station, and the other model the data from only the centre of the grid. We use two irradiance values from the forecast, the downward irradiance and the downward diffuse irradiance. These irradiance values were normalized linearly to the range $0.0-1.0$ before input into the neural network.

\subsection{Error metric}
In other work done in this area, multiple error metrics are used. One error metric is used more commonly than others, Mean Absolute Percentage Error (MAPE) \cite{lin_temporal_2020, lee_forecasting_2018, jaidee_very_2019, su_machine_2019}, which is the reason that metric was chosen.
When working with near-zero values MAPE becomes unhelpful as it is calculated by dividing by that near-zero value, so all cases where the irradiance is less than 15\% of the maximum value in the data set are dropped. Hence we do not evaluate early morning or late evening performance.
While a valuable metric, MAPE does not  fully represent the value of the model. Other factors like confidence, discussed in Section~\ref{sec:loss_function} and deviance from total irradiance for the day also represent key factors in the usefulness of the model.

@@

\section{Model}
    \subsection{Temporal Fusion Transformer}
    \textcolor{red}{TODO: more}

@@

    \subsection{Setup}
    \textcolor{red}{TODO: finish --- early stopping}\\
    We trained two models. One which utilizes weather forecast data from an area surrounding the power station, and one which does not, discussed in Section~\ref{cha:forecast_data}. The limited model is intended to show that the model is able to glean additional information from the surrounding area data.

@@

    \subsubsection{Inputs}
        The dataset was split into a training set, composing 70\% of the data, a validation set, composing 10\% of the data and finally 20\% of the data was reserved for testing.
        Figure~\ref{fig:solar_tft_overviwew} shows how the observed inputs, the irradiance measurements, along with corresponding data from historical irradiance forecasts are used as training inputs...

    \subsubsection{Tuning}
        Significant tuning was done to optimize the performance of both models. Since the goal of tuning was not only to minimize Mean Absolute Percentage Error, but balance that with the ability to recognize uncertainty, the process was very manual. Tables~\ref{tab:full_params} and \ref{tab:lim_params} show the selected hyperparameters for the full and limited models respectively.

@@

        \begin{table}[ht!]
        \begin{center}
        \caption{The full model hyperparameters.
        \label{tab:full_params}}
        \vspace{0.5cm}
        \begin{tabular}{|l|r|}
        \hline
        \textbf{Hyperparameter} & \textbf{Value} \\ \hline
        Learning rate            & 0.01         \\ \hline
        Batch size              & 24            \\ \hline
        Dropout                 & 0.1            \\ \hline
        Hidden size            & 64         \\ \hline
        Hidden continuous size & 8         \\ \hline
        Attention head size   & 1         \\ \hline
        \end{tabular}

@@

        \begin{table}[ht!]
        \begin{center}
        \caption{The limited model hyperparameters.
        \label{tab:lim_params}}
        \vspace{0.5cm}
        \begin{tabular}{|l|r|}
        \hline
        \textbf{Hyperparameter} & \textbf{Value} \\ \hline
        Learning rate            & 0.005         \\ \hline
        Batch size              & 24            \\ \hline
        Dropout                 & 0.1            \\ \hline
        Hidden size            & 40         \\ \hline
        Hidden continuous size & 6         \\ \hline
        Attention head size    & 1         \\ \hline
        \end{tabular}

@@

    \subsubsection{Loss function}\label{sec:loss_function}
    \textcolor{red}{TODO: Fix, find more sources and make sure this is correct}\\
    We use the quantile loss  Temporal Fusion Transformers is quantile loss, which we use.
    A model's prediction is a random value within a probability distribution \cite{}. If we make multiple predictions we can estimate this probability distribution by seeing within what range a selected proportion of the predictions fall \cite{koenker_quantile_2001}. PyTorch Forecasting's quantile loss function takes the Mean Absolute Error (MAE) of three quantiles, 90\%, 50\% and 10\%. [0.02, 0.1, 0.25, 0.5, 0.75, 0.9, 0.98] This gives a good picture of the model's confidence in a prediction. A smaller quantile range indicated more confidence.

>>>>

In this chapter, we discuss our solution to the problem of predicting solar power production. We cover the data we had access to and ultimately selected to train the neural network with, and how we processed and structured the data. We explain the Temporal Fusion Transformer architecture and how we set it up and use it to achieve our goals.

@@

\subsection{Irradiance measurements}
The irradiance was measured with seven Kipp \& Zonen CM21 pyranometers placed around the power station. The pyranometers have a reported maximum measurement error of 3\%. For input into the network, the highest and lowest measured values are dropped and the average value of the other five measurements is used. This data is provided with five-minute intervals, but the neural network operates hourly. To downsample the measurement data to an hourly format, we averaged the values for the twenty minutes before and after the beginning of each hour. Finally, the irradiance values were normalized linearly to the range $0.0-1.0$ before being input into the neural network.

\subsection{Forecast Data\label{cha:forecast_data}}
The weather forecast data is provided by Belgingur ehf., Reykjavík, Iceland. We use irradiance values from historical 24-hour weather forecasts generated by their WRF model, discussed in Section~\ref{cha:WRF}. The forecasts have a temporal resolution of one hour and a spatial resolution of 2.5km. One of our models uses forecast data from a 3x3 grid centred on the solar power station, and the other model the data from only the centre of the grid. We use two irradiance values from the forecast, the downward irradiance and the downward diffuse irradiance. These irradiance values were normalized linearly to the range $0.0-1.0$ before being input into the neural network.

\subsection{Error metric}
In other work done in this area, multiple error metrics are used. One error metric is used more commonly than others, Mean Absolute Percentage Error (MAPE) \cite{lin_temporal_2020, lee_forecasting_2018, jaidee_very_2019, su_machine_2019}, which is the reason that metric was chosen.
When working with near-zero values MAPE becomes unhelpful as it is calculated by dividing by that near-zero value, so all cases where the irradiance is less than 15\% of the maximum value in the data set are dropped. Hence we do not evaluate early morning or late evening performance.
While a valuable metric, MAPE does not  fully represent the function of the model. Other factors like confidence, discussed in Section~\ref{sec:loss_function} and deviance from total irradiance for the day also represent key factors in the usefulness of the model.

@@

\section{Model}
    \subsection{Temporal Fusion Transformer}
    \textcolor{red}{TODO: add more meat}

@@

    \subsection{Setup}
    We trained two models. One which utilizes weather forecast data from an area surrounding the power station, and one which does not, as discussed in Section~\ref{cha:forecast_data}. The limited model is intended to show that the full model is able to glean additional information from the surrounding area data.

@@

    \subsubsection{Inputs}
        The dataset was split into a training set, composing 70\% of the data, a validation set, composing 10\% of the data and finally, 20\% of the data was reserved for testing.
        Figure~\ref{fig:solar_tft_overviwew} shows how the observed inputs, the irradiance measurements, along with corresponding data from historical irradiance forecasts are used as training inputs.

    \subsubsection{Tuning}
        Significant tuning was done to optimize the performance of both models. Since the goal of tuning was not only to minimize Mean Absolute Percentage Error but balance that with the ability to recognize uncertainty, the process was very manual. Tables~\ref{tab:full_params} and \ref{tab:lim_params} show the selected hyperparameters for the full and limited models respectively.\\

        To avoid overfitting and to speed up the training of models, we used early stopping to stop training when the loss function optimization plateaued.

@@

        \begin{table}[ht!]
        \begin{center}
        \caption{The full model hyperparameters.
        \label{tab:full_params}}
        \vspace{0.5cm}
        \begin{tabular}{|l|r|}
        \hline
        \textbf{Hyperparameter} & \textbf{Value} \\ \hline
        Learning rate            & 0.01         \\ \hline
        Batch size              & 24            \\ \hline
        Dropout                 & 0.1            \\ \hline
        Gradient clip           & 0.1           \\ \hline
        Hidden layer size            & 64         \\ \hline
        Hidden continuous size & 8         \\ \hline
        Attention head size   & 1         \\ \hline
        \end{tabular}

@@

        \begin{table}[ht!]
        \begin{center}
        \caption{The limited model hyperparameters.
        \label{tab:lim_params}}
        \vspace{0.5cm}
        \begin{tabular}{|l|r|}
        \hline
        \textbf{Hyperparameter} & \textbf{Value} \\ \hline
        Learning rate            & 0.005         \\ \hline
        Batch size              & 24            \\ \hline
        Dropout                 & 0.1            \\ \hline
        Gradient clip           & 0.1           \\ \hline
        Hidden layer size            & 40         \\ \hline
        Hidden continuous size & 6         \\ \hline
        Attention head size    & 1         \\ \hline
        \end{tabular}

@@

    \subsubsection{Loss function}\label{sec:loss_function}
    \textcolor{red}{TODO: Flesh out and fix}\\
    We use the quantile loss  Temporal Fusion Transformers is quantile loss, which we use.
    A model's prediction is a random value within a probability distribution \cite{}. If we make multiple predictions we can estimate this probability distribution by seeing within what range a selected proportion of the predictions fall \cite{koenker_quantile_2001}. PyTorch Forecasting's quantile loss function takes the Mean Absolute Error (MAE) of three quantiles, 90\%, 50\% and 10\%. [0.02, 0.1, 0.25, 0.5, 0.75, 0.9, 0.98] This gives a good picture of the model's confidence in a prediction. A smaller quantile range indicated more confidence.

### 2022-05-08 results.tex
General fleshing out, refinement and fixes.

\chapter{Results}
Both models show a strong ability to predict solar irradiance one day into the future.
The full model, using weather forecast data from the surrounding area, shows both a lower Mean Absolute Percentage Error (MAPE), at 13.21\% vs. 15.98\%, as well as better tracking in challenging conditions and a better ability to recognize uncertain conditions, generally reporting lower confidence when its predictions are wrong. Both models can be trained to achieve slightly lower MAPE, but that comes at the cost of a higher tendency to underfit variance, and higher false confidence.
We show irradiance plots for select days representative of the models' performance in various conditions. These plots show the measured irradiance for the day, the models' predicted irradiance values, along with a 90\% confidence interval, detailed in section~\ref{sec:loss_function}. The plots also show the forecast downward shortwave irradiance, the largest factor in measured irradiance, from the model input. Additionally, the graphs contain the average MAPE for the day and the sum of prediction and observation values. The sum values act as a gauge for the total irradiance for the day.

@@

\subsection{Low variance days}
In the test dataset, there are some clear days, where the sun was mostly or entirely unobstructed. The model predicts most of these days with very low error, in the range of 2-5\%. The 90\% confidence interval stays within $\pm100 W/m^2$ for the whole day and the true prediction is almost spot-on, as can be seen in Figure~\ref{fig:full_low_best}.
\begin{figure}[ht!]
    \centering
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/low/best_3.png}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/low/best_2.png}}\qquad
    \caption{Examples of clear days where the model preforms very well.
    \label{fig:full_low_best}}
\end{figure}

The model does not manage near-perfect predictions on all of these clear days, and makes a few under-predictions, as can be seen in Figure~\ref{fig:full_low_worst}.
These predictions still predict steady sunshine, and are within the 90\% confidence interval, which is slightly larger than for the other clear day predictions. These predictions have a higher MAPE of 10-13\%.

@@

\afterpage{%
\begin{figure}[ht!]
    \centering
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/low/worst_1.png}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/low/worst_2.png}}\qquad
    \caption{Examples of clear days where the model does not perform well.
    \label{fig:full_low_worst}}
\end{figure}

\begin{figure}[ht!]
    \centering
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/medium/med_g_1.png}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/medium/med_g_2.png}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/medium/med_g_3.png}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/medium/med_g_4.png}}\qquad
    \caption{Examples of days with some drops in irradiance, where the model performs very well.
    \label{fig:full_med_best}}
\end{figure}
\clearpage
}

@@

\clearpage
\subsection{High variance days}
A few days in the dataset had very low irradiance for part of, or the whole day, or large fluctuations in irradiance. These situations are the most difficult for the model to predict. Figures~\ref{fig:full_high_a}, \ref{fig:full_high_b} and \ref{fig:full_high_c} show the model somewhat following the observations, but with a high MAPE of 38-80\% because of offsets in time and/or magnitude. The observed value is often outside the 90\% confidence interval of the predictions. For Figures~\ref{fig:full_high_a}, \ref{fig:full_high_b} the sum of predicted values is close to the sum of observed values, indicating relatively high accuracy for the days taken as a whole. Figure~mi\ref{fig:full_high_d} shows an outlier with an extremely high MAPE of 139\%, where the model predicts an almost clear day, with high confidence, on a day that received very little irradiance.
\begin{figure}[ht!]
    \centering
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/high/high_1.png}\label{fig:full_high_a}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/high/high_2.png}\label{fig:full_high_b}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/high/high_3.png}\label{fig:full_high_c}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/high/high_4.png}\label{fig:full_high_d}}\qquad
    \caption{Examples of days with large drops in irradiance or low irradiance throughout.
    \label{fig:full_high}}
\end{figure}

\clearpage
\section{Less forecast data}
To confirm that the full model utilizes the input data for the surrounding area, we also trained the model on only irradiance forecast for the cell the power station is located in.
The limited model achieves an average MAPE of 15.98\% on the test dataset. The maximum daily average MAPE is 122.87\% and the minimum is 3.47\%. Figure~\ref{fig:days_less} shows the average MAPE the limited model achieved for the test dataset on a day-by-day basis.
\begin{figure}[ht!]
    \centering
    \includegraphics[scale=1]{imgs/graphs/less/days_single.png}
    \caption{The recorded Mean Absolute Percentage Error for each day in the test dataset of the limited model. 
    \label{fig:days_less}}
\end{figure}

@@

\afterpage{%
\vspace{5cm}
\begin{figure}[ht!]
    \centering
    \makebox[\textwidth][c]{\subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/less/medium/med_g_1.png}\label{fig:less_med_a}}\qquad}
    \makebox[\textwidth][c]{\subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/less/medium/med_m_2.png}\label{fig:less_med_b}}\qquad}
    \makebox[\textwidth][c]{\subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/less/medium/med_m_1.png}\label{fig:less_med_c}}\qquad
    }
    \caption{Examples of days with some drops in irradiance.
    \label{fig:less_med}}
\end{figure}
\clearpage
}

\clearpage
\subsection{High variance days}
For the few days in the dataset that had very low irradiance for part of, or the whole day or large fluctuations in irradiance, the model displays high error, MAPE in the range 53-123\% with varying confidence. Figures~\ref{fig:less_high_a} and \ref{fig:less_high_b} show large over-predictions with high confidence, and Figures~\ref{fig:less_high_c} and \ref{fig:less_high_d} show days where the 90\% confidence interval covers the top 60\% of the graph, yet it does not cover the observations.
\begin{figure}[ht!]
    \centering
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/less/high/high_1.png}\label{fig:less_high_a}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/less/high/high_2.png}\label{fig:less_high_b}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/less/high/high_3.png}\label{fig:less_high_c}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/less/high/high_4.png}\label{fig:less_high_d}}\qquad
    \caption{Examples of days with large drops in irradiance or low irradiance throughout.
    \label{fig:less_high}}
\end{figure}

>>>>

\chapter{Results}
Both models show a strong ability to predict solar irradiance one day into the future.
The full model, using weather forecast data from the surrounding area, shows both a lower Mean Absolute Percentage Error (MAPE), at 13.21\% vs. 15.98\%, as well as better tracking in challenging conditions and a better ability to recognize uncertain conditions, generally reporting lower confidence when its predictions are wrong. Both models can be trained to achieve slightly lower MAPE, but that comes at the cost of a higher tendency to underfit variance and higher false confidence.
We show irradiance plots for select days representative of the models' performance in various conditions. These plots show the measured irradiance for the day, the models' predicted irradiance values, along with a 90\% confidence interval, detailed in section~\ref{sec:loss_function}. The plots also show the forecast downward shortwave irradiance, the largest factor in measured irradiance, from the model input. Additionally, the graphs contain the average MAPE for the day and the sum of prediction and observation values. The sum values act as a gauge for the total irradiance for the day.

@@

\subsection{Low variance days}
In the test dataset, there are some clear days, where the sun was mostly or entirely unobstructed. The model predicts most of these days with very low error, in the range of 2-5\%. The 90\% confidence interval stays within $\pm100 W/m^2$ for the whole day and the true prediction is almost spot-on, as can be seen in Figure~\ref{fig:full_low_best}.
\begin{figure}[ht!]
    \centering
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/low/best_3.png}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/low/best_2.png}}\qquad
    \caption{Examples of clear days where the model performs very well.
    \label{fig:full_low_best}}
\end{figure}

The model does not manage near-perfect predictions on all of these clear days, and makes a few under-predictions, as can be seen in Figure~\ref{fig:full_low_worst}.
These predictions still predict steady sunshine and are within the 90\% confidence interval, which is slightly larger than for the other clear day predictions. These predictions have a higher MAPE of 10-13\%.

@@

\afterpage{%
\begin{figure}
    \centering
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/low/worst_1.png}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/low/worst_2.png}}\qquad
    \caption{Examples of clear days where the model does not perform well.
    \label{fig:full_low_worst}}
\end{figure}

\begin{figure}
    \centering
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/medium/med_g_1.png}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/medium/med_g_2.png}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/medium/med_g_3.png}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/medium/med_g_4.png}}\qquad
    \caption{Examples of days with some drops in irradiance, where the model performs very well.
    \label{fig:full_med_best}}
\end{figure}
\clearpage
}

@@

\clearpage
\subsection{High variance days}
A few days in the dataset had very low irradiance for part of, or the whole day, or large fluctuations in irradiance. These situations are the most difficult for the model to predict. Figures~\ref{fig:full_high_a}, \ref{fig:full_high_b} and \ref{fig:full_high_c} show the model somewhat following the observations, but with a high MAPE of 38-80\% because of offsets in time and/or magnitude. The observed value is often outside the 90\% confidence interval of the predictions. For Figures~\ref{fig:full_high_a}, \ref{fig:full_high_b} the sum of predicted values is close to the sum of observed values, indicating relatively high accuracy for the days taken as a whole. Figure~\ref{fig:full_high_d} shows an outlier with an extremely high MAPE of 139\%, where the model predicts an almost clear day, with high confidence, on a day that received very little irradiance.
\begin{figure}[ht!]
    \centering
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/high/high_1.png}\label{fig:full_high_a}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/high/high_2.png}\label{fig:full_high_b}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/high/high_3.png}\label{fig:full_high_c}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/full/high/high_4.png}\label{fig:full_high_d}}\qquad
    \caption{Examples of days with large drops in irradiance or low irradiance throughout.
    \label{fig:full_high}}
\end{figure}

\clearpage
\section{Less forecast data}
To confirm that the full model utilizes the input data for the surrounding area, we also trained the model on only the irradiance forecast for the cell the power station is located in.
The limited model achieves an average MAPE of 15.98\% on the test dataset. The maximum daily average MAPE is 122.87\% and the minimum is 3.47\%. Figure~\ref{fig:days_less} shows the average MAPE the limited model achieved for the test dataset on a day-by-day basis.
\begin{figure}[ht!]
    \centering
    \includegraphics[scale=1]{imgs/graphs/less/days_single.png}
    \caption{The recorded Mean Absolute Percentage Error for each day in the test dataset of the limited model. 
    \label{fig:days_less}}
\end{figure}

@@

\afterpage{%
\vspace{5cm}
\begin{figure}
    \centering
    \makebox[\textwidth][c]{\subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/less/medium/med_g_1.png}\label{fig:less_med_a}}\qquad}
    \makebox[\textwidth][c]{\subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/less/medium/med_m_2.png}\label{fig:less_med_b}}\qquad}
    \makebox[\textwidth][c]{\subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/less/medium/med_m_1.png}\label{fig:less_med_c}}\qquad
    }
    \caption{Examples of days with some drops in irradiance.
    \label{fig:less_med}}
\end{figure}
\clearpage
}

\clearpage
\subsection{High variance days}
For the few days in the dataset that had very low irradiance for part of, or the whole day, or large fluctuations in irradiance, the model displays a high error, MAPE in the range 53-123\% with varying confidence. Figures~\ref{fig:less_high_a} and \ref{fig:less_high_b} show large over-predictions with high confidence, and Figures~\ref{fig:less_high_c} and \ref{fig:less_high_d} show days where the 90\% confidence interval covers the top 60\% of the graph, yet it does not cover the observations.
\begin{figure}[ht!]
    \centering
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/less/high/high_1.png}\label{fig:less_high_a}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/less/high/high_2.png}\label{fig:less_high_b}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/less/high/high_3.png}\label{fig:less_high_c}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/less/high/high_4.png}\label{fig:less_high_d}}\qquad
    \caption{Examples of days with large drops in irradiance or low irradiance throughout.
    \label{fig:less_high}}
\end{figure}
